Designing Large-Scale Imaging Surveys for a Retrospective Relative Photometric Calibration

### 2012-08-24 paper/self_calibration_I.tex
add analysis region

In this paper, we have considered the design of survey strategies for calibrating the large-scale, relative photometric response of an instrument, but there are many more calibration parameters that can be constrained from this method. For example, the optical distortion of an instrument or the point-spread-function variation could also be constrained with such a method, although it would need to be explored whether the properties of a survey strategy that makes it good for one calibration, are also suitable for other calibration aspects; ultimately a trade-off would need to be performed between the different calibration concerns and the other goals of the survey, such as sky coverage, variability monitoring and so-on.

\acknowledgments
It is a pleasure to thank Rob Fergus (NYU), Jason Kalirai (STScI),
and Sam Roweis (deceased) for valuable conversations.

>>>>

In this paper, we have considered the design of survey strategies for calibrating the large-scale, relative photometric response of an instrument, but there are many more calibration parameters that can be constrained from this method. For example, the optical distortion of an instrument or the point-spread-function variation could also be constrained with such a method, although it would need to be explored whether the properties of a survey strategy that makes it good for one calibration, are also suitable for other calibration aspects.

HOGG write van Dokkum paragraph
Ultimately a trade-off would need to be performed between the different calibration concerns and the other goals of the survey, such as sky coverage, variability monitoring and so-on.

\acknowledgments
It is a pleasure to thank Rob Fergus (NYU), Jason Kalirai (STScI), Sam Roweis (deceased), and Pieter van Dokkum (Yale) for valuable conversations.
